A bad day of studying is better than a good day of sleeping

### 2020-12-24 paper/paper.tex
feat: better scatterplot

    \begin{figure}
        \centering
        \begin{tikzpicture}
            \begin{axis}[
                  yticklabels={,,$x_{4}$,$x_{3}$,$x_{2}$,$x_{1}$},
                  xticklabels={,,},
                  ytick style={draw=none},
                  xtick style={draw=none},
                  axis line style={draw=none},
            scatter/classes={
                empty={mark=o,draw=black}}]
                    \addplot[scatter,
                        scatter src=explicit symbolic]
                        table [meta=label] {
                    x y label

                    5 1 empty
                    7 1 empty

                    2 2 empty
                    4 2 empty

                    2 3 empty
                    4 3 empty

                    1 4 empty
                    3 4 empty
                    };
            \end{axis}
        \end{tikzpicture}
        \label{plot:example-visualisation-scatterplot}
            \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
    \end{figure}
\end{example}

>>>>

    \begin{figure}
        \centering
        \begin{tikzpicture}[scale=1.2]
            \begin{axis}[
                  yticklabels={,,$x_{4}$,$x_{3}$,$x_{2}$,$x_{1}$},
                  xticklabels={,,},
                  ytick style={draw=none},
                  xtick style={draw=none},
                  axis line style={draw=none}
            ]
            \addplot[
                scatter,
                scatter src=explicit symbolic,
                mark size=3,
                scatter/classes={
                    empty={mark=o, draw=black},
                    filled={mark=x, draw=black}
                },
                nodes near coords*={\Label},
                visualization depends on={value \thisrow{label} \as \Label}
            ]
            table [meta=class] {
                    x y class label

                    5 1 empty $x_{4}^{+}$
                    7 1 empty $x_{4}^{-}$

                    2 2 empty $x_{3}^{+}$
                    4 2 empty $x_{3}^{-}$

                    2 3 empty $x_{2}^{+}$
                    4 3 empty $x_{2}^{-}$

                    1 4 empty $x_{1}^{+}$
                    3 4 empty $x_{1}^{-}$
                    };
            \end{axis}
        \end{tikzpicture}
        \label{plot:example-visualisation-scatterplot}
            \caption{Representation of $\preceq$ over $W^{\pm}$ using sticks}
    \end{figure}
\end{example}
